Batch Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design

### 2018-02-09 paper/intro.tex
Paper update

% TODO: Traditional methods using offline model and simulated based methods are
% not good
The analog circuit design automation problems can be formulated as optimization
problems. The aim is to find the optimal design parameters that provide
the best circuit performance, which can be represented by a figure of merit (FOM)
scalar real-valued function. Prior works about analog circuit optimization include offline
model-based approaches
~\cite{colleran2003optimization,daems2003simulation,wang2014enabling} and
simulation-based approaches. The offline model-based methods try to build
accurate global models of the FOM and then optimize the cheap-to-evaluate models. The
problem of this approach is that the accurate models are usually hard to get.
For example, in~\cite{wang2014enabling}, 100,000 randomly simulated points are
used to train a sparse polynomial model for an amplifier circuit with ten
design parameters.

@@

% TODO: Bayesian optimization is a sequential algorithm, there is a need to
% parallelize it
%
% TODO: cite the two 3D-IC papers of TVLSI
To reduce the number of circuit simulations, the Gaussian process
(GP)~\cite{GPML} model has been introduced as an online surrogate model to
assist the optimization. In~\cite{liu2014gaspad}, GP is combined with
differential evolution algorithm. Recently, the
Bayesian optimization (BO)~\cite{shahriari2016taking} algorithm has been
applied for analog circuit optimization. In~\cite{lyu2017efficient}, the Bayesian optimization algorithm is
firstly introduced for the single- and multi-objective optimization of general analog circuits and has
shown to be more efficient compared with other simulation-based
approaches. In~\cite{wang2017efficient}, the Bayesian optimization algorithm
is combined with adaptive Monte-Carlo sampling to optimize the yield of analog
circuits and static random-access memory (SRAM).

@@

The Bayesian optimization algorithm has been extended to enable batch
selection. Some prior works, like the qEI \cite{qEI}, qKG \cite{wu2016parallel}
and parallel predictive entropy search (PPES)~\cite{shah2015parallel}
approaches, consider to search for the optimal batch selection for a given
acquisition function. These methods usually involve some approximations or
Monte-Carlo sampling, and thus scales poorly as the batch size increases. Other
works, including the simulation matching (SM)~\cite{azimi2010batch} method, the
batch-UCB (BUCB, BLCB for minimization
problems)~\cite{desautels2014parallelizing} method, the parallel UCB with pure
exploration (GP-UCB-PE)~\cite{contal2013parallel} method and the local
penalization (LP)~\cite{gonzalez2016batch} method, adopted the \emph{greedy}
strategies that select individual points until the batch is filled.

% TODO: Beiefly introduce my algorithm
All the algorithms mentioned above choose to use single acquisition function.
And except for the SM method~\cite{azimi2010batch} and LP method~\cite{gonzalez2016batch} which can use arbitrary acquisition
function, other parallelization methods rely on a specific acquisition
function. The UCB acquisition function must be used for BUCB and GP-UCB-PE, and
the knowledge gradient (KG) acquisition function must be used for the qKG algorithm. As is stated
in~\cite{hoffman2011portfolio}, no single acquisition function can always
outperform other acquisition functions. Relying on one acquisition function may
result in poor performance.

>>>>

% TODO: Traditional methods using offline model and simulated based methods are
% not good
The analog circuit design automation problems can be formulated as optimization
problems. The aim is to find the optimal design parameters that provide the
best circuit performance, which can be represented by a figure of merit (FOM)
scalar real-valued function. Prior works about analog circuit optimization
include offline model-based approaches
~\cite{colleran2003optimization,daems2003simulation,wang2014enabling} and
simulation-based approaches. The offline model-based methods try to build
global models of the FOM via manual calculation or regression with simulated
data and then optimize the cheap-to-evaluate models. The problem with this
approach is that the accurate models are usually hard to get. For example,
in~\cite{wang2014enabling}, 100,000 randomly simulated points are used to train
a sparse polynomial model for an amplifier circuit with ten design parameters.

@@

% TODO: Bayesian optimization is a sequential algorithm, there is a need to
% parallelize it

In recent years, the Gaussian process (GP)~\cite{GPML} model has been
introduced for the automated design of analog circuits to reduce the
required number of circuit simulations. In~\cite{liu2014gaspad}, GP is combined
with differential evolution algorithm. Recently, the Bayesian optimization
(BO)~\cite{shahriari2016taking} algorithm has also been applied for analog
circuit optimization. In~\cite{lyu2017efficient}, the Bayesian optimization
algorithm is firstly introduced for the single- and multi-objective
optimization of general analog circuits and has shown to be more efficient
compared with other simulation-based approaches. In~\cite{wang2017efficient},
the Bayesian optimization algorithm is combined with adaptive Monte-Carlo
sampling to optimize the yield of analog circuits and static random-access
memory (SRAM).

@@

The Bayesian optimization algorithm has been extended to enable batch
selection. Some prior works, like the qEI \cite{qEI}, qKG \cite{wu2016parallel}
and parallel predictive entropy search (PPES)~\cite{shah2015parallel}
approaches, consider to search for the optimal batch selection for a given
acquisition function. These methods usually involve some approximations or
Monte-Carlo sampling, and thus scales poorly as the batch size increases. Other
works, including the simulation matching (SM)~\cite{azimi2010batch} method, the
batch-UCB (BUCB, BLCB for minimization
problems)~\cite{desautels2014parallelizing} method, the parallel UCB with pure
exploration (GP-UCB-PE)~\cite{contal2013parallel} method, and the local
penalization (LP)~\cite{gonzalez2016batch} method, adopted the \emph{greedy}
strategies that select individual points until the batch is filled.

% TODO: Beiefly introduce my algorithm
All the batch Bayesian optimization algorithms mentioned above choose to use single acquisition function.
And except for the SM method~\cite{azimi2010batch} and LP method~\cite{gonzalez2016batch} which can use arbitrary acquisition
function, other parallelization methods rely on a specific acquisition
function. The UCB acquisition function must be used for BUCB and GP-UCB-PE, and
the knowledge gradient (KG) acquisition function must be used for the qKG algorithm. As is stated
in~\cite{hoffman2011portfolio}, no single acquisition function can always
outperform other acquisition functions. Relying on one acquisition function may
result in poor performance.
